---
title: "EDS 212 Day 2 Tasks"
author: "Elise Gonzales"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)

```

```{r}
ex_1 <- expression(x ^ 2)
my_derivative <- deriv(ex_1, "x")
x <- 3
eval(my_derivative)
```

```{r}
ex_2 <- expression(2 * ((3 * a + 2) ^ 4) - 5)
my_deriv_2 <- deriv(ex_2, "a")
a <- 1.2
eval(my_deriv_2)
```

```{r}

ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm)) + geom_point(aes(color = species)) + labs(x = "Bill length (mm)", y = "Bill depth (mm)", title = "Palmer penguin size measurements")

```

In a new code chunk, make a jitterplot of flipper length by species (species on the x-axis, flipper length on the y-axis). Update axis labels and add a title.

Knit your .Rmd to check for reproducibility

Stage, commit, and push changes to the remote repo. Once you do, go to GitHub and check to see the changes are safely stored & tracked.

Go back to your R Markdown document in RStudio. Pull to make sure you have the same versions as in the remote repo. Make a change (anything you want - maybe change your graph colors, sizes, etc.), then stage, commit, & push changes to the remote repo to reinforce the steps. Check that changes are stored on GitHub.

Repeat two more times - make changes to your plot, knit, stage, commit & push. Check that your changes appear on GitHub.

